POMDP comparisons across sigma_m, sigma_g

### 2017-10-05 appendix/appendix.Rmd
solution with discount 0.99 resolves initialization issues

```{r}
#alphas <- alphas_from_log(meta, log_dir)
```

@@

```{r pomdp_sims}
# slower!
pomdp_sims <- 
  map2_dfr(models, alphas, function(.x, .y){
             sim_pomdp(.x$transition, .x$observation, .x$reward, discount, 
                       unif_prior, x0 = x0, Tmax = Tmax, alpha = .y,
                       reps=reps)$df %>% 
              mutate(method = "pomdp") # include a column labeling method
           },
           .id = "scenario") %>% left_join(meta)
```

>>>>

```{r}
log_dir <- "../pomdp_intro"
meta <- meta_from_log("pomdp_intro", log_dir)
alphas <- alphas_from_log(meta, log_dir)
```

@@

```{r pomdp_sims}
# slower!
unif_prior <- rep(1, length(states)) / length(states)
pomdp_sims <- 
  map2_dfr(models, alphas, function(.x, .y){
             sim_pomdp(.x$transition, .x$observation, .x$reward, discount, 
                       unif_prior, x0 = x0, Tmax = Tmax, alpha = .y,
                       reps=reps)$df %>% 
              mutate(method = "pomdp") # include a column labeling method
           },
           .id = "scenario") %>% left_join(meta)
```
